Lasso_RCI_Response

### 2024-03-25 Lasso_RCI_Response.Rmd
Updated RCI table

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
# #Demographics Table
# Demo_tab_df <- Mothership_post |>
#   #Mothership_Diag_treat |>
#   filter(!is.na(Education_1),
#          !is.na(Race_1),
#          !is.na(Gender_1),
#          !is.na(Disorder_Type),
#          !is.na(Relationship_1),
#          !is.na(RESPONDER_FIGS)
#         )

# #Demographic tab
# Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
# colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
# Demo_tab
# 
# Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
# colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
# Simple_Demo_tab
# 
# Table

Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  )

Vars_anx <- Mothership_lasso |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

# Mothership_lasso_dep <- Mothership_post |>
#     filter(
#     !is.na(Some_College),
#     !is.na(Female),
#     !is.na(IPT_track_1),
#     !is.na(White),
#     !is.na(Depression_Responder),
#     CUXOS_pre >= 20,
#     CUDOS_pre >= 20
#   )

Vars_dep <- Mothership_lasso |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

Vars_anx <- na.omit(Vars_anx)
Vars_dep <- na.omit(Vars_dep)

@@

## Vector of variables to summarize
table1_vars_anx <- c(colnames(Vars_anx)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
tab1_df_anx <- data.frame(table1_tab_anx)
tab1_df_anx
### next gather info based upon depression

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D", "Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
table1_tab_dep

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
table1_gen

@@

JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
# Depresssion
JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))

@@

@@

Vars_dep <- na.omit(Vars_dep)

>>>>

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
    Anxiety_Responder, Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))

Mothership_lasso <- na.omit(Mothership_lasso)

summary(Mothership_lasso$Anxiety_Responder)

# Vars_dep <- Mothership_lasso |>
#   select( c(
#     Depression_Responder,
#     # Demographics
#     Age_1,Some_College:Married,White, 
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, 
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre,
#     # RDQ
#     rdqPOST_coping:rdqPOST_wbs
#   ))

@@

## Vector of variables to summarize
table1_vars_anx <- c(colnames(Mothership_lasso)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx
### next gather info based upon depression

@@

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D",        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
table1_tab_dep

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
write_csv(table1_gen,"~/Downloads/table1_gen.csv")
table1_gen

@@

JT_table[1,] = c("CUXOS", unlist(summary(Vars_anx$Anxiety_Responder)))
# Depresssion
JT_table[2,] = c("CUDOS", unlist(summary(Vars_dep$Depression_Responder)))

@@

summary(Vars_dep$Depression_Responder)

@@

Vars_dep <- na.omit(Vars_dep)
```
